Anomaly_inspection

### 2021-01-18 anomaly.Rmd
Visualize the missing data using naniar package

library(tidyverse)
library(brolgar)
```

@@

ggplot(top12) +
  geom_line(aes(x = year,
                y = mean_hourly_wage)) +
  facet_wrap(~id)
```

@@

ggplot(bottom12) +
  geom_line(aes(x = year,
                y = mean_hourly_wage)) +
  facet_wrap(~id)
```

@@

ggplot(random) +
  geom_line(aes(x = year,
                y = mean_hourly_wage)) +
  facet_wrap(~id)

@@

ggplot(top20_comp) +
  geom_line(aes(x = year,
                y = mean_hourly_wage)) +
  facet_wrap(~id)

@@

ggplot(bottom20_comp) +
  geom_line(aes(x = year,
                y = mean_hourly_wage)) +
  facet_wrap(~id)
```

@@

ggplot(random2) +
  geom_line(aes(x = year,
                y = mean_hourly_wage)) +
  facet_wrap(~id)
```

>>>>

library(tidyverse)
library(brolgar)
library(naniar)
```

@@

ggplot(top12, 
       aes(x = year,
           y = mean_hourly_wage)) +
  geom_miss_point() +
  geom_line() +
  facet_wrap(~id)
```

@@

ggplot(bottom12,
       aes(x = year,
           y = mean_hourly_wage)) +
  geom_miss_point() +
  geom_line() +
  facet_wrap(~id)
```

@@

ggplot(random, 
       aes(x = year,
                y = mean_hourly_wage)) +
  geom_miss_point() +
  geom_line() +
  facet_wrap(~id)

@@

ggplot(top20_comp,
       aes(x = year,
                y = mean_hourly_wage)) +
  geom_miss_point() +
  geom_line()+
  facet_wrap(~id)

@@

ggplot(bottom20_comp,
       aes(x = year,
                y = mean_hourly_wage)) +
  geom_miss_point() +
  geom_line() +
  facet_wrap(~id)
```

@@

ggplot(random2,
       aes(x = year,
                y = mean_hourly_wage)) +
  geom_miss_point() +
  geom_line() +
  facet_wrap(~id)
```
